---
title: "Understanding Moves Toward Immigration Populism"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(primer.data)
library(rstanarm)

# Consider someone whose att_end at the end of the experiment is 1 or more units
# greater than their att_start. They become more conservative on immigration
# issues. Consider such people to have made a meaningful move toward immigration
# populism. Let's use `move_to_pop` as a new variable, defined as TRUE for such
# people. We are interested to see if two variables might be associated with
# move_to_pop: treatment and age.

x <- trains %>% 
  mutate(move_to_pop = ifelse(att_end >= att_start + 1, TRUE, FALSE)) %>% 
  select(move_to_pop, treatment, age)
```



What is the causal effect of the treatment on the probability of becoming more populist?

-compare treatment to control 
-what population is he asking about? sample would have to be representative of the population
-small sample size (115)

Fit Model:
move_to_pop ~ treatment
y_i = beta_0 + beta_1 * treatment + epsilon_i

```{r}

fit_1 <- stan_glm(data = x,
                  formula = move_to_pop ~ treatment,
                  family = binomial, 
                  refresh = 0,
                  seed = 65)
```

```{r}

newobs <- tibble(treatment = c("Treated", "Control"))

pe <- posterior_epred(fit_1, 
                      newdata = newobs) %>% 
  as_tibble() %>%
  mutate(ate = `1` - `2`)

```

```{r}

pe %>% 
  ggplot(aes(x = ate)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100) +
    labs(title = "Posterior for Average Treatment Effect",
         subtitle = "Treatment makes people about 20% more likely to be populist",
         x = "Difference in Attitude",
         y = "Probability") +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()

pe

```

If we assign the treatment to 25 people, how many will become more populist?

```{r}
newobs1 <- tibble(treatment = c(rep("Treated", 25)))

pp <- posterior_predict(fit_1, 
                        newdata = newobs1) %>%
    as_tibble() %>%
    mutate_all(as.numeric) %>%
    rowwise() %>% 
    mutate(total = sum(c_across()))
  
pp
```


```{r}
pp %>% 
  ggplot(aes(x = total)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100)  +
    labs(title = "Posterior for Number of People who Became More Populist",
         subtitle = "Likely that 10 of the next 25 become more populist",
         x = "Number",
         y = "Probability") +
    scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic()
```

